---
title: "Plots for simulation scenarios with 80 confidence interval"
author: "Xinru WANG"
date: "2024-02-06"
output: html_document
editor_options: 
chunk_output_type: console
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# clean environment 
rm(list = ls())

# set working directory to the `practical/` folder 
wd = "/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/"
#wd = '~/Documents/GitHub/practical/'
setwd(wd)

# load libraries and functions
scripts = paste0(wd, 'Code/Functions/', list.files(paste0(wd, 'Code/Functions/')))
lapply(scripts, source)

# load data in the output folder 
files = list.files(path = paste0(wd, 'Code/Run_output'), full.names = TRUE, pattern = "iter1000_2024-02-04.rds")
power_t1_files = grep('power_|t1_', files)
if (length(power_t1_files) > 0) {files = files[-grep('power_|t1_', files)]}
outputs = list()
for (file in files){
  outputs[[sub('.*/', '', file)]] = readRDS(file)
}

# get names of methods
all_names = names(outputs[[1]][[1]]$scenario_out[[1]])
all_method_names = all_names[grep('method', all_names)]

method_labs = rep(NA, length(all_method_names))
method_labs[grep('method_1', all_method_names)] = "Fixed-effect (frequentist)"
method_labs[grep('method_1_', all_method_names)] = "Fixed-effect (Bayesian, "
method_labs[grep('method_2', all_method_names)] = "Mixed-effect (frequentist)"
method_labs[grep('method_2_', all_method_names)] = "Mixed-effect (Bayesian, "
method_labs[grep('NI', all_method_names)] = paste0(method_labs[grep('NI', all_method_names)], 'non-informative prior)')
method_labs[endsWith(all_method_names, 'str')] = paste0(method_labs[endsWith(all_method_names, 'str')], 'strongly-informative prior)')
method_labs[endsWith(all_method_names, 'wk')] = paste0(method_labs[endsWith(all_method_names, 'wk')], 'weakly-informative prior)')
method_labs[endsWith(all_method_names, 'str_ur1')] = paste0(method_labs[endsWith(all_method_names, 'str_ur1')], 'strongly-informative/UR1 prior)')
method_labs[endsWith(all_method_names, 'str_ur2')] = paste0(method_labs[endsWith(all_method_names, 'str_ur2')], 'strongly-informative/UR2 prior)')
method_labs[endsWith(all_method_names, 'wk_ur1')] = paste0(method_labs[endsWith(all_method_names, 'wk_ur1')], 'weakly-informative/UR1 prior)')
method_labs[endsWith(all_method_names, 'wk_ur2')] = paste0(method_labs[endsWith(all_method_names, 'wk_ur2')], 'weakly-informative/UR2 prior)')

n_methods = length(method_labs)
shapes = 1:n_methods # methods differentiated by shapes 
names(shapes) = method_labs

# get names of treatments
tx_labs = rownames(outputs[[1]][[1]]$scenario_out[[1]]$est_method_1_wk)
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
colors_list = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals))) 
colors = c("#7FC97F", "#BEAED4", "#FDC086", "#386CB0") 
#sample(colors_list, length(tx_labs))
names(colors) = tx_labs

font_size = 22
pt_size = 2
N_iter = 1000
```
## Final analysis report {.tabset .tabset-fade .tabset-pills}

### Bias, Coverage, MSE

#### Scenario 1.1
All treatments have equal effects: 
  Tj = 37.5%, j = A, B, C, D

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.1 = grep('1.1', files,fixed = TRUE)
if (length(ind1.1) == 1) {
  plot_biasmse(Scenario = '1.1', d = outputs[[ind1.1]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 1.2
Treatment B is better than treatments A, C and D: 
  $T_B = 35\%$; and 
$T_j = 45\%$, $j = A, C, D$
  
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

ind1.2 = grep('1.2', files,fixed = TRUE)
if (length(ind1.2) == 1) {
  plot_biasmse(Scenario = '1.2', d = outputs[[ind1.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}



#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.2_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.3
All 4 treatments have different effects (small difference):
  $T_A = 30\%$; $T_B = 35\%$; $T_C = 40\%$; $T_D = 45\%$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.3 = grep('1.3', files,fixed = TRUE)
if (length(ind1.3) == 1) {
  plot_biasmse(Scenario = '1.3', d = outputs[[ind1.3]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.4
All 4 treatments have different effects (large difference):
  TA = 30%; TB = 40%; TC = 50%; TD = 60%
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.4 = grep('1.4', files,fixed = TRUE)
if (length(ind1.4) == 1) {
  plot_biasmse(Scenario = '1.4', d = outputs[[ind1.4]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.5
All 4 treatments have different effects (small difference):
  $T_A = 35\%$; $T_B = 30\%$; $T_C = 45\%$; $T_D = 40\%$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.5 = grep('1.5', files,fixed = TRUE)
if (length(ind1.5) == 1) {
  plot_biasmse(Scenario = '1.5', d = outputs[[ind1.5]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.6
Treatment B is worst than treatments A, C and D: 
  $T_B = 45\%$; and 
$T_j = 35\%$, $j = A, C, D$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.6 = grep('1.6', files,fixed = TRUE)
if (length(ind1.6) == 1) {
  plot_biasmse(Scenario = '1.6', d = outputs[[ind1.6]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.1
Tj = 17.5%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.1 = grep('2.1', files,fixed = TRUE)
if (length(ind2.1) == 1) {
  plot_biasmse(Scenario = '2.1', d = outputs[[ind2.1]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.2
TA = 10%, TB = 15%, TC = 20%, TD = 25%

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.2 = grep('2.2', files,fixed = TRUE)
if (length(ind2.2) == 1) {
  plot_biasmse(Scenario = '2.2', d = outputs[[ind2.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.3
Tj = 82.5%, j = A, B, C, D

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.3 = grep('2.3', files,fixed = TRUE)
if (length(ind2.3) == 1) {
  plot_biasmse(Scenario = '2.3', d = outputs[[ind2.3]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.4
TA = 75%, TB = 80%, TC = 85%, TD = 90%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.4 = grep('2.4', files,fixed = TRUE)
if (length(ind2.4) == 1) {
  plot_biasmse(Scenario = '2.4', d = outputs[[ind2.4]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 3.1
Tj = 37.5%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind3.1 = grep('3.1', files,fixed = TRUE)
if (length(ind3.1) == 1) {
  plot_biasmse(Scenario = '3.1', d = outputs[[ind3.1]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 3.2
TA = 30%, TB = 35%, TC = 40%, TD = 45%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind3.2 = grep('3.2', files,fixed = TRUE)
if (length(ind3.2) == 1) {
  plot_biasmse(Scenario = '3.2', d = outputs[[ind3.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.1
Different effectiveness across patterns:
Pattern 1: Tj = 30%, j = A, B, C, D
Pattern 2: Tj = 35%, j = A, B, C, D
Pattern 3: Tj = 40%, j = A, B, C, D
Pattern 4: Tj = 45%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.1 = grep('4.1', files,fixed = TRUE)
if (length(ind4.1) == 1) {
  plot_biasmse(Scenario = '4.1', d = outputs[[ind4.1]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.2
Different effectiveness across patterns:
Pattern 1: $T_A = 19.9%$, $T_B = 25.0%$, $T_C = 29.9%$, $T_D = 35.0%$
Pattern 2: $T_A = 29.1%$, $T_B = 35.4%$, $T_C = 41.3%$, $T_D = 47.0%$
Pattern 3: $T_A = 64.8%$, $T_B = 71.1%$, $T_C = 76.0%$, $T_D = 79.9%$
Pattern 4: $T_A = 83.3%$, $T_B = 87.0%$, $T_C = 89.6%$, $T_D = 91.5%$

  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.2 = grep('4.2', files,fixed = TRUE)
if (length(ind4.2) == 1) {
  plot_biasmse(Scenario = '4.2', d = outputs[[ind4.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.3
Different treatment effects in 8 sites compares to the other 2 sites: 
TAq = 30%, TBq = 35% TCq = 40% TDq = 45%, q = 3, …, 10; and 
TAq = 20%, TBq = 25%, TCq = 30%, TDq = 35%, q = 1, 2

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.3 = grep('4.3', files,fixed = TRUE)
if (length(ind4.3) == 1) {
  plot_biasmse(Scenario = '4.3', d = outputs[[ind4.3]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```



### Mortality gain

#### Scenario 1.2
Treatment B is better than treatments A, C and D: 
  $T_B = 35\%$; and 
$T_j = 45\%$, $j = A, C, D$
  
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind1.2 = grep('1.2', files,fixed = TRUE)
if (length(ind1.2) == 1) {
  plot_mort(Scenario = '1.2', d = outputs[[ind1.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.2_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.3
All 4 treatments have different effects (small difference):
  $T_A = 30\%$; $T_B = 35\%$; $T_C = 40\%$; $T_D = 45\%$
  
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind1.3 = grep('1.3', files,fixed = TRUE)
if (length(ind1.3) == 1) {
  plot_mort(Scenario = '1.3', d = outputs[[ind1.3]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 1.4
All 4 treatments have different effects (large difference):
  TA = 30%; TB = 40%; TC = 50%; TD = 60%
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width =18}

ind1.4 = grep('1.4', files,fixed = TRUE)
if (length(ind1.4) == 1) {
  plot_mort(Scenario = '1.4', d = outputs[[ind1.4]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.5
All 4 treatments have different effects (small difference):
  $T_A = 35\%$; $T_B = 30\%$; $T_C = 45\%$; $T_D = 40\%$
  
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind1.5 = grep('1.5', files,fixed = TRUE)
if (length(ind1.5) == 1) {
  plot_mort(Scenario = '1.5', d = outputs[[ind1.5]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.6
Treatment B is worst than treatments A, C and D: 
  $T_B = 45\%$; and 
$T_j = 35\%$, $j = A, C, D$
  
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind1.6 = grep('1.6', files,fixed = TRUE)
if (length(ind1.6) == 1) {
  plot_mort(Scenario = '1.6', d = outputs[[ind1.6]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.2
TA = 10%, TB = 15%, TC = 20%, TD = 25%
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind2.2 = grep('2.2', files,fixed = TRUE)
if (length(ind2.2) == 1) {
  plot_mort(Scenario = '2.2', d = outputs[[ind2.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.4
TA = 75%, TB = 80%, TC = 85%, TD = 90%
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind2.4 = grep('2.4', files,fixed = TRUE)
if (length(ind2.4) == 1) {
  plot_mort(Scenario = '2.4', d = outputs[[ind2.4]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 3.2
TA = 30%, TB = 35%, TC = 40%, TD = 45%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind3.2 = grep('3.2', files,fixed = TRUE)
if (length(ind3.2) == 1) {
  plot_mort(Scenario = '3.2', d = outputs[[ind3.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}
#ggsave(paste0(wd,"Code/Plots/biasmse_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 4.1
Different effectiveness across patterns:
Pattern 1: Tj = 30%, j = A, B, C, D
Pattern 2: Tj = 35%, j = A, B, C, D
Pattern 3: Tj = 40%, j = A, B, C, D
Pattern 4: Tj = 45%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind4.1 = grep('4.1', files,fixed = TRUE)
if (length(ind4.1) == 1) {
  plot_mort(Scenario = '4.1', d = outputs[[ind4.1]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.2
Different effectiveness across patterns:
Pattern 1: $T_A = 19.9%$, $T_B = 25.0%$, $T_C = 29.9%$, $T_D = 35.0%$
Pattern 2: $T_A = 29.1%$, $T_B = 35.4%$, $T_C = 41.3%$, $T_D = 47.0%$
Pattern 3: $T_A = 64.8%$, $T_B = 71.1%$, $T_C = 76.0%$, $T_D = 79.9%$
Pattern 4: $T_A = 83.3%$, $T_B = 87.0%$, $T_C = 89.6%$, $T_D = 91.5%$

```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind4.2 = grep('4.2', files,fixed = TRUE)
if (length(ind4.2) == 1) {
  plot_mort(Scenario = '4.2', d = outputs[[ind4.2]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.3
Different treatment effects in 8 sites compares to the other 2 sites: 
TAq = 30%, TBq = 35% TCq = 40% TDq = 45%, q = 3, …, 10; and 
TAq = 20%, TBq = 25%, TCq = 30%, TDq = 35%, q = 1, 2

```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}

ind4.3 = grep('4.3', files,fixed = TRUE)
if (length(ind4.3) == 1) {
  plot_mort(Scenario = '4.3', d = outputs[[ind4.3]])
} else {
  message('There are multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/mort_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```



### Power

#### Scenario 1.2
Treatment B is better than treatments A, C and D: 
  $T_B = 35\%$; and 
$T_j = 45\%$, $j = A, C, D$
  
```{r, echo = FALSE, fig.align="center",fig.height = 6, fig.width = 12}
ind1.2 = grep('1.2', files,fixed = TRUE)
if (length(ind1.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.2', d = outputs[[ind1.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.2]])))
  }
  # plot 
  plot_type2(Scenario = '1.2', plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.2_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.3
All 4 treatments have different effects (small difference):
  $T_A = 30\%$; $T_B = 35\%$; $T_C = 40\%$; $T_D = 45\%$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.3 = grep('1.3', files,fixed = TRUE)
if (length(ind1.3) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.3]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.3', d = outputs[[ind1.3]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.3]])))
  }
  # plot 
  plot_type2(Scenario = '1.3', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 1.4
All 4 treatments have different effects (large difference):
  TA = 30%; TB = 40%; TC = 50%; TD = 60%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.4 = grep('1.4', files,fixed = TRUE)
if (length(ind1.4) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.4]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.4', d = outputs[[ind1.4]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.4]])))
  }
  # plot 
  plot_type2(Scenario = '1.4', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 1.5
All 4 treatments have different effects (small difference):
  $T_A = 35\%$; $T_B = 30\%$; $T_C = 45\%$; $T_D = 40\%$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.5 = grep('1.5', files,fixed = TRUE)
if (length(ind1.5) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.5]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.5', d = outputs[[ind1.5]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.5]])))
  }
  # plot 
  plot_type2(Scenario = '1.5', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.6
Treatment B is worst than treatments A, C and D: 
  $T_B = 45\%$; and 
$T_j = 35\%$, $j = A, C, D$
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.6 = grep('1.6', files,fixed = TRUE)
if (length(ind1.6) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.6]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.6', d = outputs[[ind1.6]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.6]])))
  }
  # plot 
  plot_type2(Scenario = '1.6', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```
#### Scenario 2.2
TA = 10%, TB = 15%, TC = 20%, TD = 25%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.2 = grep('2.2', files,fixed = TRUE)
if (length(ind2.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind2.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '2.2', d = outputs[[ind2.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind2.2]])))
  }
  # plot 
  plot_type2(Scenario = '2.2', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.4
TA = 75%, TB = 80%, TC = 85%, TD = 90%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.4 = grep('2.4', files,fixed = TRUE)
if (length(ind2.4) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind2.4]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '2.4', d = outputs[[ind2.4]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind2.4]])))
  }
  # plot 
  plot_type2(Scenario = '2.4', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 3.2
TA = 30%, TB = 35%, TC = 40%, TD = 45%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind3.2 = grep('3.2', files,fixed = TRUE)
if (length(ind3.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind3.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '3.2', d = outputs[[ind3.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind3.2]])))
  }
  # plot 
  plot_type2(Scenario = '3.2', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 4.2
Different effectiveness across patterns:
Pattern 1: $T_A = 19.9%$, $T_B = 25.0%$, $T_C = 29.9%$, $T_D = 35.0%$
Pattern 2: $T_A = 29.1%$, $T_B = 35.4%$, $T_C = 41.3%$, $T_D = 47.0%$
Pattern 3: $T_A = 64.8%$, $T_B = 71.1%$, $T_C = 76.0%$, $T_D = 79.9%$
Pattern 4: $T_A = 83.3%$, $T_B = 87.0%$, $T_C = 89.6%$, $T_D = 91.5%$

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.2 = grep('4.2', files,fixed = TRUE)
if (length(ind4.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind4.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '4.2', d = outputs[[ind4.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind4.2]])))
  }
  # plot 
  plot_type2(Scenario = '4.2', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.3
Different treatment effects in 8 sites compares to the other 2 sites: 
TAq = 30%, TBq = 35% TCq = 40% TDq = 45%, q = 3, …, 10; and 
TAq = 20%, TBq = 25%, TCq = 30%, TDq = 35%, q = 1, 2

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.3 = grep('4.3', files,fixed = TRUE)
if (length(ind4.3) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind4.3]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '4.3', d = outputs[[ind4.3]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind4.3]])))
  }
  # plot 
  plot_type2(Scenario = '4.3', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


### Type 1 error

#### Scenario 1.1

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

ind1.1 = grep('1.1', files,fixed = TRUE)
if (length(ind1.1) == 1) {
  
  t1_filename = paste0('t1_', sub('.*/', '', files[[ind1.1]]))
  if (t1_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', t1_filename))
  } else {
    plot.d = get_type1(Scenario = '1.1', d = outputs[[ind1.1]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/t1_", sub('.*/', '', files[[ind1.1]])))
  }
  #plot 
 plot_type1(plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/type1_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

Bests by pattern 
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest_alt(outputs, .font_size, .pt_size, N_iter, ind = ind1.1)

```
Overall best
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest(outputs, .font_size, .pt_size, N_iter, ind = ind1.1)

```

#### Scenario 2.1
Tj = 17.5%, j = A, B, C, D

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

ind2.1 = grep('2.1', files,fixed = TRUE)
if (length(ind2.1) == 1) {
  
  t1_filename = paste0('t1_', sub('.*/', '', files[[ind2.1]]))
  if (t1_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', t1_filename))
  } else {
    plot.d = get_type1(Scenario = '2.1', d = outputs[[ind2.1]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/t1_", sub('.*/', '', files[[ind2.1]])))
  }
  # plot 
  plot_type1(plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/type1_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

Bests by pattern 
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest_alt(outputs, .font_size, .pt_size, N_iter, ind = ind2.1)
```

Overall best
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest(outputs, .font_size, .pt_size, N_iter, ind = ind2.1)
```


#### Scenario 2.3
Tj = 82.5%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

ind2.3 = grep('2.3', files,fixed = TRUE)
if (length(ind2.3) == 1) {
  
  t1_filename = paste0('t1_', sub('.*/', '', files[[ind2.3]]))
  if (t1_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', t1_filename))
  } else {
    plot.d = get_type1(Scenario = '2.3', d = outputs[[ind2.3]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/t1_", sub('.*/', '', files[[ind2.3]])))
  }
  # plot 
  plot_type1(plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/type1_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

Bests by pattern
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest_alt(outputs, .font_size, .pt_size, N_iter, ind = ind2.3)
```

Overall best
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest(outputs, .font_size, .pt_size, N_iter, ind = ind2.3)
```

#### Scenario 3.1
Tj = 37.5%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

ind3.1 = grep('3.1', files,fixed = TRUE)
if (length(ind3.1) == 1) {
  
  t1_filename = paste0('t1_', sub('.*/', '', files[[ind3.1]]))
  if (t1_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', t1_filename))
  } else {
    plot.d = get_type1(Scenario = '3.1', d = outputs[[ind3.1]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/t1_", sub('.*/', '', files[[ind3.1]])))
  }
  # plot 
  plot_type1(plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}

#ggsave(paste0(wd,"Code/Plots/type1_scenario1.1_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

Bests by pattern 
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest_alt(outputs, .font_size, .pt_size, N_iter, ind = ind3.1)
```

Overall best
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest(outputs, .font_size, .pt_size, N_iter, ind = ind3.1)
```


#### Scenario 4.1
Different effectiveness across patterns:
Pattern 1: Tj = 30%, j = A, B, C, D
Pattern 2: Tj = 35%, j = A, B, C, D
Pattern 3: Tj = 40%, j = A, B, C, D
Pattern 4: Tj = 45%, j = A, B, C, D
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.1 = grep('4.1', files,fixed = TRUE)
if (length(ind4.1) == 1) {
  
  t1_filename = paste0('t1_', sub('.*/', '', files[[ind4.1]]))
  if (t1_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', t1_filename))
  } else {
    plot.d = get_type1(Scenario = '4.1', d = outputs[[ind4.1]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/t1_", sub('.*/', '', files[[ind4.1]])))
  }
  # plot 
  plot_type1(plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}
```

Bests by pattern 
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest_alt(outputs, .font_size, .pt_size, N_iter, ind = ind4.1)
```

Overall best
```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

 plot_nullbest(outputs, .font_size, .pt_size, N_iter, ind = ind4.1)
```


### Identify the best

#### Scenario 1.2
Treatment B is better than treatments A, C and D: 
  $T_B = 35\%$; and 
$T_j = 45\%$, $j = A, C, D$
  
```{r, echo = FALSE, fig.align="center",fig.height = 12, fig.width = 18}
ind1.2 = grep('1.2', files,fixed = TRUE)
if (length(ind1.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.2', d = outputs[[ind1.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.2]])))
  }
  # plot 
  plot_best(Scenario = '1.2', plot.d)
} else {
  message('There are no or multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.2_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.3
All 4 treatments have different effects (small difference):
  $T_A = 30\%$; $T_B = 35\%$; $T_C = 40\%$; $T_D = 45\%$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.3 = grep('1.3', files,fixed = TRUE)
if (length(ind1.3) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.3]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.3', d = outputs[[ind1.3]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.3]])))
  }
  # plot 
  plot_best(Scenario = '1.3', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 1.4
All 4 treatments have different effects (large difference):
  TA = 30%; TB = 40%; TC = 50%; TD = 60%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.4 = grep('1.4', files,fixed = TRUE)
if (length(ind1.4) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.4]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.4', d = outputs[[ind1.4]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.4]])))
  }
  # plot 
  plot_best(Scenario = '1.4', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 1.5
All 4 treatments have different effects (small difference):
  $T_A = 35\%$; $T_B = 30\%$; $T_C = 45\%$; $T_D = 40\%$
  
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.5 = grep('1.5', files,fixed = TRUE)
if (length(ind1.5) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.5]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.5', d = outputs[[ind1.5]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.5]])))
  }
  # plot 
  plot_best(Scenario = '1.5', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 1.6
Treatment B is worst than treatments A, C and D: 
  $T_B = 45\%$; and 
$T_j = 35\%$, $j = A, C, D$
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind1.6 = grep('1.6', files,fixed = TRUE)
if (length(ind1.6) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind1.6]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '1.6', d = outputs[[ind1.6]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind1.6]])))
  }
  # plot 
  plot_best(Scenario = '1.6', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.2
TA = 10%, TB = 15%, TC = 20%, TD = 25%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.2 = grep('2.2', files,fixed = TRUE)
if (length(ind2.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind2.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '2.2', d = outputs[[ind2.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind2.2]])))
  }
  # plot 
  plot_best(Scenario = '2.2', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 2.4
TA = 75%, TB = 80%, TC = 85%, TD = 90%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind2.4 = grep('2.4', files,fixed = TRUE)
if (length(ind2.4) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind2.4]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '2.4', d = outputs[[ind2.4]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind2.4]])))
  }
  # plot 
  plot_best(Scenario = '2.4', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 3.2
TA = 30%, TB = 35%, TC = 40%, TD = 45%
```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind3.2 = grep('3.2', files,fixed = TRUE)
if (length(ind3.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind3.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '3.2', d = outputs[[ind3.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind3.2]])))
  }
  # plot 
  plot_best(Scenario = '3.2', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


#### Scenario 4.2
Different effectiveness across patterns:
Pattern 1: $T_A = 19.9%$, $T_B = 25.0%$, $T_C = 29.9%$, $T_D = 35.0%$
Pattern 2: $T_A = 29.1%$, $T_B = 35.4%$, $T_C = 41.3%$, $T_D = 47.0%$
Pattern 3: $T_A = 64.8%$, $T_B = 71.1%$, $T_C = 76.0%$, $T_D = 79.9%$
Pattern 4: $T_A = 83.3%$, $T_B = 87.0%$, $T_C = 89.6%$, $T_D = 91.5%$

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.2 = grep('4.2', files,fixed = TRUE)
if (length(ind4.2) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind4.2]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '4.2', d = outputs[[ind4.2]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind4.2]])))
  }
  # plot 
  plot_best(Scenario = '4.2', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```

#### Scenario 4.3
Different treatment effects in 8 sites compares to the other 2 sites: 
TAq = 30%, TBq = 35% TCq = 40% TDq = 45%, q = 3, …, 10; and 
TAq = 20%, TBq = 25%, TCq = 30%, TDq = 35%, q = 1, 2

```{r, echo = FALSE, fig.align="center", fig.height = 14, fig.width = 18}

ind4.3 = grep('4.3', files,fixed = TRUE)
if (length(ind4.3) == 1) {
  
  power_filename = paste0('power_', sub('.*/', '', files[[ind4.3]]))
  if (power_filename %in% list.files('Code/Run_output/')) {
    # retrieve data if file already present 
    plot.d = readRDS(paste0(wd, 'Code/Run_output/', power_filename))
  } else {
    plot.d = get_type2(Scenario = '4.3', d = outputs[[ind4.3]])
    saveRDS(plot.d, paste0(wd, "Code/Run_output/power_", sub('.*/', '', files[[ind4.3]])))
  }
  # plot 
  plot_best(Scenario = '4.3', plot.d)
} else {
  message('There are multiple output files in `output`. Please select one.')
}


#ggsave(paste0(wd,"Code/Plots/type2_scenario1.3_", Sys.Date(), ".pdf"), f, width = 8, height = 7)

```


### Running time

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}
# plot running time
files_timing = list.files(path = paste0(wd, 'Code/Run_output'), full.names = TRUE, pattern = "^timing_")
scenario = str_extract(files_timing, "\\d+\\.\\d+") 
scenario. = c("1.1","1.2","1.3","1.4","1.5","1.6",
              "2.1","2.2","2.3","2.4",
              "3.1","3.2",
              "4.1","4.2","4.3")
files_timing = files_timing[which(scenario %in% scenario.)]
outputs_timing = rep(NA,length(files_timing))

for (i in 1:length(files_timing)){
  outputs_timing[i] = readRDS(files_timing[i])
}

plot_timing(Scenario = scenario., Timing=outputs_timing)
```


### Errors and Warning

```{r}
lapply(outputs, function(x){
  lapply(x, function(y){
    y$analyse_out$display_warn
  })
})

lapply(outputs, function(x){
  lapply(x, function(y){
    y$analyse_out$display_error
  })
})
```



### Coefficient Estimates 

#### Scenario 1.1 -- Method 1  

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

###plot coefficient estimates for scenario 1.1, 1.6, 4.2 

ind1.1 = grep('1.1', files,fixed = TRUE)

if(length(ind1.1) == 1){
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind1.1, method = "Method 1", Scenario = "1.1")
}else{
 message('There are multiple output files in `output`. Please select one.')
}

```


#### Scenario 1.1 -- Method 1 Strong 

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}
if(length(ind1.1) == 1){
ind1.1 = grep('1.1', files,fixed = TRUE)
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind1.1, method = "Method 1 Strong", Scenario = "1.1")
}else{
 message('There are multiple output files in `output`. Please select one.')
}
```

#### Scenario 1.1 -- Method 1 Strong UR2  

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

if(length(ind1.1) == 1){
ind1.1 = grep('1.1', files,fixed = TRUE)
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind1.1, method = "Method 1 Strong UR2", Scenario = "1.1")
}else{
 message('There are multiple output files in `output`. Please select one.')
}

```


#### Scenario 1.6 -- Method 1  

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}
ind1.6 = grep('1.6', files,fixed = TRUE)

if(length(ind1.6) == 1){
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind1.6, method = "Method 1", Scenario = "1.6")
}else{
message('There are multiple output files in `output`. Please select one.')
}

```


#### Scenario 1.6 -- Method 1 Strong 

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

if(length(ind1.6) == 1){
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind1.6, method = "Method 1 Strong", Scenario = "1.6")
}else{
message('There are multiple output files in `output`. Please select one.')
}

```


#### Scenario 1.6 -- Method 1 Strong UR2  

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

if(length(ind1.6) == 1){
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind1.6, method = "Method 1 Strong UR2", Scenario = "1.6")
}else{
message('There are multiple output files in `output`. Please select one.')
}
```

#### Scenario 4.2 -- Method 1  

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}
ind4.2 = grep('4.2', files,fixed = TRUE)

if(length(ind4.2) == 1) {
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind4.2, method = "Method 1", Scenario = "4.2")
}else{
 message('There are multiple output files in `output`. Please select one.')
}

```

####Scenario 4.2 -- Method 1 Strong 

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}

if(length(ind4.2) == 1) {
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind4.2, method = "Method 1 Strong", Scenario = "4.2")
}else{
 message('There are multiple output files in `output`. Please select one.')
}
```


####Scenario 4.2 -- Method 1 Strong UR2

```{r, echo = FALSE, fig.align="center",fig.height = 14, fig.width = 18}
if(length(ind4.2) == 1) {
plot_coef_distrib(outputs, .font_size, .pt_size, N_iter, ind = ind4.2, method = "Method 1 Strong UR2", Scenario = "4.2")
}else{
 message('There are multiple output files in `output`. Please select one.')
}

```
