---
title: "Simulation for investigating the effect of patterns"
author: "Xinru Wang"
date: "2024-03-21"
output: html_document
editor_options: 
chunk_output_type: console
---

## Simulation under two scenarios {.tabset .tabset-fade .tabset-pills}

 + The frequentist mixed effect models have similar coverage as the fixed effect models. However, the bayesian mixed effect models have much higher coverage rate compared with the fixed effect models. The reason may be that there are something wrong in the specified prior distribution.
 
#### Compare bayesian mixed effect models with strong prior (est_method_2_str) and default prior in stan (est_method_2_non)

We compare est_method_2_str and est_method_2_non with sample size 500 under two settings:

Pattern 1 pattern list: pattern_list = list(pattern1 = c(2, 3), pattern2 = c(1, 2, 3), pattern3 = c(2, 3, 4), pattern4 = c(1, 2, 3, 4));

Pattern 2 pattern list: pattern_list = list(pattern1 = c(1, 2, 3, 4), pattern2 = c(1, 2, 3, 4), pattern3 = c(1, 2, 3, 4), pattern4 = c(1, 2, 3, 4));

For Pattern 1  and the est_method_2_str:


```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.1_iter100_2024-03-20.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```

For Pattern 1 and the est_method_2_non:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_non
```

We can see that for Pattern 1, phi2 has a higher coverage rate.

For Pattern 2 and the est_method_2_str:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.1_iter100_2024-03-20_pattern_same.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```
 
For Pattern 2 and the est_method_2_non:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_non
```
 
We can see that for Pattern 2, phi1 has a higher coverage rate.

####  The mixed effect models have smaller bias than the fixed effect models. Why? 

#### The bias of mixed effect models under scenario 4.2 are much higher than fixef effect models. Why?