---
title: "Simulation for investigating the effect of patterns"
author: "Xinru Wang"
date: "2024-03-21"
output: html_document
editor_options: 
chunk_output_type: console
---

 
## Compare bayesian mixed effect models

We compare est_method_2, est_method_2_str, est_method_1, and est_method_1_str with sample size 500 simulation time 500 under two settings:

Pattern 1 pattern list: pattern_list = list(pattern1 = c(2, 3), pattern2 = c(1, 2, 3), pattern3 = c(2, 3, 4), pattern4 = c(1, 2, 3, 4));

Pattern 2 pattern list: pattern_list = list(pattern1 = c(1, 2, 3, 4), pattern2 = c(1, 2, 3, 4), pattern3 = c(1, 2, 3, 4), pattern4 = c(1, 2, 3, 4));

### scenario 1.1

For Pattern 1  and the est_method_2:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.1_iter500.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```

For Pattern 1 and the est_method_2_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_str
```

For Pattern 1 and fixed effect frequentist methods:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1
```

For Pattern 1 and fixed effect bayesian methods:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1_str
```

For Pattern 2 and the est_method_2:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.1_iter500_pattern_same.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```
 
For Pattern 2 and the est_method_2_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_str
```
 
For Pattern 2 and est_method_1:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1
```

For Pattern 2 and est_method_1_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1_str
```


### scenario 1.3

For Pattern 1  and the est_method_2:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.3_iter500.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```

For Pattern 1 and the est_method_2_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_str
```

For Pattern 1 and est_method_1:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1
```

For Pattern 1 and est_method_1_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1_str
```

For Pattern 2 and the est_method_2:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.3_iter500_pattern_same.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```
 
For Pattern 2 and the est_method_2_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_str
```

For Pattern 2 and est_method_1:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1
```

For Pattern 2 and est_method_1_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1_str
```

### scenario 1.6

For Pattern 1  and the est_method_2:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.6_iter500.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```

For Pattern 1 and the est_method_2_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_str
```

For Pattern 1 and est_method_1:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1
```

For Pattern 1 and est_method_1_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1_str
```

For Pattern 2 and the est_method_2:

```{r, echo = FALSE}
output <- readRDS("/Users/cheryl/Documents/duke-nus/bibhas/practical/practical/Code/Run_output/scenarioscenario1.6_iter500_pattern_same.rds")
output$`for size size = 500`$analyse_out$method.property$est_method_2
```
 
For Pattern 2 and the est_method_2_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_2_str
```

For Pattern 2 and est_method_1:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1
```

For Pattern 2 and est_method_1_str:

```{r, echo = FALSE}
output$`for size size = 500`$analyse_out$method.property$est_method_1_str
```
